A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-04 manuscript.Rmd
explaint how to reproduce a project close #22 related #25

>>>>

## Reproduce a Project

A reproducible project should not only be theoretically reproducible, but it should be simple to reproduce.
Ideally, you have a statement in the README that contains a few steps to reproduce the project, where most steps are automatic and standardized.
This statement should also note the required software.
E.g. you can download any git repository with these commands:

``` bash
# this should be run in the terminal
git clone https://github.com/aaronpeikert/repro-tutorial.git
cd repro-tutorial
```

Projects that combine Make and Docker then can usually be reproduced with:

``` bash
# this should be run in the terminal
make docker &&
make -B DOCKER=TRUE 
```

<!-- maybe we add here the real data? #25 -->
